Assessment of climate change impacts on hydro resources in Três Marias reservoir using machine learning models

### 2021-04-27 paper/paper.tex
Remoção dos erros e avisos para a entrega 2

% TODO: preencher citação, transformar 'ONS (2020)' em citação
Over 63\% of the whole electricity supply in Brazil came from hydropower in 2019. However, Brazil faces reduced availability of hydro resources in recent years. ONS affirmed that Brazil is experiencing a drought period similar to the period between 1948 to 1955 \cite{onsseca}, while other studies suggested the occurrence of more frequent and anomalous droughts in Brazil due to climate changes.

@@

\begin{table}[htbp]
\centering
\caption{Variables in the related bibliograpy}
\label{tab:variables-literature}
    \begin{tabulary}{\textwidth}{lCCC}
        \toprule
           & Kassem et al (2019) & Bhatta et al (2019) & Essenfelder et al (2020) \\
        \midrule
            Precipitation & X & X & X \\
            Temperature & X & X & X \\
            Relative humidity & X &  & \\
            Wind speed  & X &  & \\
            Landuse classes  &  & X & \\
            Stream flow  & X & X & X \\
        \bottomrule
    \end{tabulary}
\end{table}

\cite{kicsi2007streamflow} presented a comparison between four different neural networks algorithms applied in short term daily stream flow forecast. They concluded that the Levenberg–Marquardt algorithm, when compared with backpro pagation, conjugate gradient and cascade correlation takes a relatively small time for training, while giving the best stream flow forecast, even using correlation analysis as the method to determine the input vector. Concurrently, \cite{petty2018streamflow} assessed the capacity of employing machine learning techniques and big data to impute streamflow using historical and real-time data. Their results demonstrated that applying Streamflow Hydrology Estimate using Machine Mearning (SHEM) models could be used to estimate streamflow and even to help fill missing data from historical datasets.

>>>>

Over 63\% of the whole electricity supply in Brazil came from hydropower in 2019. However, Brazil faces reduced availability of hydro resources in recent years. ONS affirmed that Brazil is experiencing a drought period similar to the period between 1948 to 1955 \cite{onsseca}, while other studies suggested the occurrence of more frequent and anomalous droughts in Brazil due to climate changes.

@@

\begin{table}[htbp]
\centering
\caption{Variables in the related bibliography}
\label{tab:variables-literature}
    \begin{tabulary}{\textwidth}{lCCC}
        \toprule
           & Kassem et al (2019) & Bhatta et al (2019) & Essenfelder et al (2020) \\
        \midrule
            Precipitation & X & X & X \\
            Temperature & X & X & X \\
            Relative humidity & X &  & \\
            Wind speed  & X &  & \\
            Landuse classes  &  & X & \\
            Stream flow  & X & X & X \\
        \bottomrule
    \end{tabulary}
\end{table}

\cite{kicsi2007streamflow} presented a comparison between four different neural networks algorithms applied in short term daily stream flow forecast. They concluded that the Levenberg–Marquardt algorithm, when compared with backpro pagation, conjugate gradient and cascade correlation takes a relatively small time for training, while giving the best stream flow forecast, even using correlation analysis as the method to determine the input vector. Concurrently, \cite{petty2018streamflow} assessed the capacity of employing machine learning techniques and big data to impute streamflow using historical and real-time data. Their results demonstrated that applying Streamflow Hydrology Estimate using Machine Learning (SHEM) models could be used to estimate streamflow and even to help fill missing data from historical datasets.
